Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
3.2 Formal Model

$P$ is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}. The hardware cost of $P$ is given by Eq.~\eqref{hardware-costs}

@@

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\eqref{software-communication-costs}

@@

\vspace{2 mm}
\textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}. In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related. Therefore, the objective function is:}

>>>>

$P$ is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $, \cite{Arato2003}. The hardware cost of $P$ is given in Eq.~\eqref{hardware-costs}

@@

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given in Eq.~\eqref{software-communication-costs}

@@

\vspace{2 mm}
\textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}. In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the objective is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related. Therefore, the objective function is:}
